---
title: "Precis of Coin Exchange"
author: "Cunhonghu Ding"
date: "20181017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
```

# Coin Exchange 
## - coin exchange market data, charts and forecast 
<br>
Coin Exchange is your window into the world of cryptocurrency, bringing you real-time prices and historical charts for various coins. You can add your favourite cryptocurrencies to a handy watchlist, making it easy to follow the coins that are most relevant to you. You can also create charts based on your own needs. You can even analysis the cryptocurrency market with rich data in the capital market.  

## Data Sources
<br>
Coin Prices https://coinmetrics.io/data-downloads/
<br>
Bletchley indexes data https://www.bletchleyindexes.com/downloads
<br>
U.S. Dollar Index https://fred.stlouisfed.org/series/DTWEXB
<br>
Gold Price https://fred.stlouisfed.org/series/GOLDAMGBD228NLBM
<br>
S&P 500 https://fred.stlouisfed.org/series/SP500

## Data Sample
```{r echo=FALSE}
#read data
btc <- read.csv("btc.csv")
eth <- read.csv("eth.csv")
ltc <- read.csv("ltc.csv")
index_t <- read.csv("bletchley_total.csv")
sp500 <- read.csv("SP500.csv")
usd <- read.csv("DTWEXB.csv")
gold <- read.csv("GOLDAMGBD228NLBM.csv")
knitr::kable(tail(btc))
```



